Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-03 authorinstr_2.tex

\section{Single tweet analysis}
\subsection{Data enrichment}
\subsection{Sentiment analysis}
\subsection{Concept extraction}
\subsection{Metadata analysis (opt)}

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{user modeling}
\subsection{Classification}
\subsection{Tag based analysis}
\subsection{Event identification}

>>>>

\section{Single tweet analysis}
In this section we will discuss the different types of analysis that can be done on one single tweet. This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets. 
\subsection{Data enrichment}
At the very basis of a tweet is data enrichment. Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about. To get a better understanding of the meaning of a tweet, a context is needed. For humans this is done by linking the information from the tweet to earlier acquired knowledge.\\
Some tweets contain an URL, this makes it possible for a computer to create a context from the linked resource. This works 
\subsection{Sentiment analysis}
\subsection{Concept extraction}
\subsection{Metadata analysis (opt)}

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{User Modelling}
\subsection{User Classification}

\subsection{Tag based analysis}
\subsection{Event identification}
